---
title: "Comparative Disaster Risk Modelling Methodologies"
author: "Hamish Patten, Max Loake and David Steinsaltz"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract



## Introduction

## Models

### Regression-based Models

Introduction to Generalized Linear Models (GLMs), then explaining the roles of link functions, etc.

- Poisson model
- Negative-binomial model
- log-normal
- Gamma
- Zero-inflated Poisson
- Zero-inflated negative-binomial
- Hurdle model?

### Machine Learning Models

#### Spatial Point Data

- Gaussian Process Regression (GPR) for the building damage assessment data
- Support Vector Machines

#### Spatial Raster Data

- CNNs of various hyperparameters and layers (including ResNet?)
- Generative Neural Networks?
- Convolutional Long Term Short Memory (LTSM) network

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
